Universal Anonymous Signatures

### 2022-04-13 prism-backend/research/gsac/construction-uas.tex
Added generic construction of UAS. Seems ok.

\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
\begin{itemize}
\item Parse \secpar as $(\Csecpar,\NIZKsecpar,\SBCMsecpar,\Esecpar,\AttrSpace)$
\item $\Cparm \gets \CSetup(\Csecpar)$
\item $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$
\item $\Sparm \gets \SSetup(\Ssecpar)$  
\item $\Eparm \gets \ESetup(\Esecpar)$
\item $\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$
\item $\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$
\item $\NIZKcrs_{\Inspect} \gets \NIZKSetup^{\NIZKRel_{\Inspect}}(\NIZKsecpar)$
\item Return $(\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
  \NIZKcrs_{\Sign},\NIZKcrs_{\Inspect},\AttrSpace)$
\end{itemize}

\paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
\begin{itemize}
\item Parse \parm as $(\cdot,\SBCMparm,\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$
\item $(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$
\item $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$  
\item $\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$
\item $\ipk \gets (\Svk,\fissue,\sig_{\fissue})$
\item $\isk \gets \Ssk$
\item Return $(\ipk,\isk)$
\end{itemize}

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
\begin{itemize}
\item Parse \parm as $(\cdot,\cdot,\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$
\item $(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$
\item $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$
\item $\sig_{\finsp} \gets \SSign(\Ssk,\finsp)$
\item $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$
\item $\osk \gets (\Ssk,\Edk)$
\item Return $(\opk,\osk)$
\end{itemize}

\paragraph{$\usk \gets \UKeyGen(\parm)$.} %
\begin{itemize}
\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar,\AttrSpace)$
\item $\usk \getr \AttrSpace$
\item Return \usk
\end{itemize}

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\ldblbrace (\cred_i,\ipk_i)\rdblbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\upk,\attrs,\ldblbrace \ipk_i \rdblbrace_{i \in \Issuers},\attrs)
  \rangle$.} %
To obtain a new credential, a user with secret key usk and credentials $\cred_i$,
issued by issuers with public keys $\ipk_i$, requests a signature on commitments
of both the user key and a new random credential identifier -- similarly to
\GSAC. In addition, the user proves that the issuance function \fissue
established by the issuer is satisfied by the $\cred_i$ credentials and its user
secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace (\usk,
\credid,\scred), (\Ccom,\attrs): \Ccom = \CCommit((\usk,\credid)) \land
\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred, \usk \in \cred
\rbrace$. \todo{Refine the notation for $\attr \in \cred$. Also, need to make
  the {\ipk}s explicit in it.} The interactive protocol from a user to obtain a
credential from an issuer of the system is as follows:

@@

\paragraph{$\sig \gets \Sign(\gpk,\usk,\cred,\msg,\feval)$.} %
We define the NP language $\LangSig = \lbrace (\upk,\cred,\y):
\SVerify(\sig,\upk) = 1~\land~\Ec = \EEnc(\Eek,\y)~\land~
\y = \finsp(\feval(\upk,\cred,\msg),\upk,\cred,\msg)\rbrace$. The
signing algorithm is defined as follows:
\todo{Argue that the composition of \finsp and \feval is not redundant even
  though both depend on the same arguments. Namely, because \feval is defined
  on a per-signature basis (akin to the policies of ACs), and \finsp is defined
  once per group (akin to the open function in GSs). Hence, \finsp cannot just
  be defined to ``contain'' \feval at setup time.}

\begin{itemize}
\item Parse \gpk as $(\ipk,\opk)$
\item Parse \ipk as $(\RSvk,\fissue,\sig_{\fissue})$; Verify $\sig_{\fissue}$
\item Parse \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$; Verify $\sig_{\finsp}$
\item $\sig' \gets \SSign(\usk,\msg)$
%\item $b \gets \feval(\upk,\cred,\msg)$
\item % If $b=0$: 
  $\y \gets \finsp(\feval(\upk,\cred,\msg),
  \upk,\cred,\msg)$%; else $\y = \bot$.
\item $\Ec \gets \EEnc(\Eek,\y)$
\item $\SPKproof^{\LangSig} \gets \SPKProve^{\LangSig}(\msg,(\Ec,\sig'),
  (\upk,\cred,\y))$
\item Return $(\Ec,\sig',\SPKproof^{\LangSig})$
\end{itemize}

\paragraph{$1/0 \gets \Verify(\gpk,\sig,\msg,\feval)$.} %
\begin{itemize}
\item Parse \sig as $(\Ec,\sig',\SPKproof^{\LangSig})$
\item Return $\SPKVerify^{\LangSig}(\SPKproof^{\LangSig},\msg,(\Ec,\sig'))$ 
\end{itemize}

\paragraph{$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg,\feval)$.} %

We follow the approach of \cite{bsz05} for verifiable openings. Namely, we
define an NP language $\LangVerIns = \lbrace (\Eek,\Edk,r):
(\Eek,\Edk) = \EKeyGen(\Esecpar;r) \land \y = \EDec(\Edk,\c) \rbrace$.

\begin{itemize}
\item Parse \osk as $(\Ssk,\Edk)$; \gpk as
  $(\cdot,(\Svk,\Eek,\finsp,\sig_{\finsp}))$
\item  $1 \stackrel{?}{=} \Verify(\gpk,\sig,\msg,\feval)$  
\item $\y \gets \EDec(\Edk,\c)$
\item $\NIZKproof^{\LangVerIns} \gets \NIZKProve(\NIZKcrs,(\c,\y),(\Eek,\Edk,r))$
\item Return $\NIZKproof^{\LangVerIns}$
\end{itemize}

\paragraph{$1/0 \gets \Judge(\gpk,\y,\iproof,\sig,\msg)$.} %

\begin{itemize}
\item  $1 \stackrel{?}{=} \Verify(\gpk,\sig,\msg,\feval)$
\item Parse \sig as $(\c,\cdot,\cdot)$  
\item Return $\NIZKVerify(\NIZKcrs,\iproof,(\c,\y))$
\end{itemize}

>>>>

\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
The setup process essentially consists on generating the public parameters
for all the building blocks. In detail, it parses \secpar as $(\Csecpar,
\NIZKsecpar,\SBCMsecpar,\Esecpar,\AttrSpace)$. Then, run $\Cparm \gets
\CSetup(\Csecpar)$, $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$, $\Sparm \gets
\SSetup(\Ssecpar)$, $\Eparm \gets \ESetup(\Esecpar)$, $\NIZKcrs_{\Issue} \gets
\NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$, $\NIZKcrs_{\Sign} \gets
\NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$, and $\NIZKcrs_{\Inspect} \gets
\NIZKSetup^{\NIZKRel_{\Inspect}}(\NIZKsecpar)$. Return $(\Cparm,\SBCMparm,
\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Inspect},
\AttrSpace)$

\paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
To generate its key pair, each issuer first parses \parm as $(\cdot,\SBCMparm,
\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets
\SKeyGen(\Sparm)$, $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$,
$\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\Svk,\fissue,
\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
To generate its key pair, each inspectur first parses \parm as $(\cdot,\cdot,
\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
(\Sparm)$, $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, $\sig_{\finsp} \gets \SSign
(\Ssk,\finsp)$, $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk \gets
(\Ssk,\Edk)$. Finally, returns $(\opk,\osk)$.

\paragraph{$\usk \gets \UKeyGen(\parm)$.} %
Each user, prior to requesting credentials, generates his secret key by parsing
\parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\AttrSpace)$, and picking randomly
$\usk \getr \AttrSpace$. Finally, return \usk.

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\scred,\attrs)\rangle$.} %
To obtain a new credential, a user with secret key usk and credentials $\cred_i$,
issued by issuers with public keys $\ipk_i$, requests a signature on commitments
of both the user key and a new random credential identifier -- similarly to
\GSAC. In addition, the user proves that the issuance function \fissue
established by the issuer is satisfied by the $\cred_i$ credentials and its user
secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace (\usk,
\credid,\scred), (\Ccom,\attrs): \Ccom = \CCommit((\usk,\credid)) \land
\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred, \usk \in \cred
\rbrace$. \todo{Refine the notation for $\attr \in \cred$. Also, need to make
  the {\ipk}s explicit in it.} The interactive protocol from a user to obtain a
credential from an issuer of the system is as follows:

@@

\paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of the following relation:
$\NIZKRel_{\Sign} = \lbrace (\usk,\scred,\yinsp),(\msg,\feval,\yeval,\Ec,\sipk)
: \Ec = \EEnc(\Eek,\yinsp) \land \yeval = \feval(\usk,\scred,\msg) \land
\yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk,\cred,\attrs_{\cred} \cup \lbrace \usk,\credid \rbrace) = 1)
\rbrace$, where we make two syntax abuses, to ease readability: with
$\attrs_{\cred}$ we refer to the attributes in credential \cred, which its
legitimate owner can recover easily (e.g., from secure storage); and, as stated
before, $\ipk_{\cred}$ denotes the issuer public key of credential \cred, which
we also assume to be easily recoverable from \cred, by its legitimate owner.
\todo{Maybe, try to think of clearer naming conventions.}
%
From this, in order to produce a valid signature, the user first evaluates
$\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
with the signing process -- this may depend, e.g., on the inspection policy of
\opk, as the output of \feval may influence whether the user will be
de-anonymizable or not, depending on the \finsp function in \opk.
%
Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
\Eek by running $\Ec \gets \EEnc(\Eek,\yeval)$. Finally, the user computes
$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
\yinsp))$ and  outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.

\paragraph{$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval)$.} %
The ``cryptographic'' side of the verification essentially consists on checking
the NIZK proof. That is, parse \sig as $(\NIZKproof,\Ec)$ and check whether
$\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,\sipk)) = 1$. In
addition, the verifier may further check whether \yeval meets its needs.

\paragraph{$(\yinsp,\NIZKproof)/\bot \gets
  \Inspect(\osk,\sipk,\sig,\yeval,\msg,\feval)$.} %
We first define NIZK relation $\NIZKRel_{\Inspect} = \lbrace (\osk),(\Ec,\yinsp)
: \yinsp = \EDec(\osk,\Ec) \rbrace$.
%
For inspection, the inspector first verifies the signature by running $\Verify(
\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the verification succeeds, it parses
\sig as $(\NIZKproof,\Ec)$, decrypts \Ec by running $\yeval \gets \EDec(\osk,
\Ec)$, and computes $\NIZKproof_{\Inspect} \gets \NIZKProve^{\NIZKRel_{\Inspect}}
(\NIZKcrs_{\Inspect},(\osk),(\Ec,\yinsp))$. It returns $(\yinsp,
\NIZKproof_{\Inspect})$.

\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\sig,\yeval,\msg)$.} %
To assess the validity of an inspection proof, first check the signature
by running $\Verify(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the check succeeds,
parse \sig as $((\cdot,\Ec),\cdot)$ and verify \NIZKproof with $\NIZKVerify
(\NIZKcrs_{\Inspect},\NIZKproof,(\Ec,\yinsp))$. Accept it the NIZK verification
passes, and reject otherwise.
